\documentclass[10pt]{article}
\usepackage[T1]{fontenc}
\usepackage[tmargin=2.5cm,bmargin=2.5cm]{geometry}
\usepackage{bibtopic}
\usepackage{url}

\oddsidemargin -0in
\evensidemargin -0in
\textwidth=165mm
\textheight=228mm
\parindent 0pt

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\newcommand{\mysec}[1]{\vspace{2em}\textsc{\large #1}\vspace{1mm}\hrule\vspace{2mm}}
\newcommand{\mysub}[3]{\textbf{#1} {#2} \hfill {\em #3}}
\newcommand{\myssub}[1]{\hspace*{2mm}\parbox{163mm}{#1}\vspace*{2mm}}

\begin{document}

\begin{center}
{\Large \textbf{\textsc{Baris Kasikci}}} \vspace{1mm} \\
{\em Associate Professor} \\
Paul G. Allen School of Computer Science \& Engineering \\
University of Washington
\end{center}

\vspace{1em}

\hspace{0.8in}
\begin{tabular}{@{}p{2.5in}p{4in}}
University of Washington\\
Box 352350 & Seattle, WA 98195-2350\\
baris@cs.washington.edu & \url{http://bariskasikci.org/} \\
\end{tabular}


\mysec{Research Interests}

My research is centered around building efficient and trustworthy computer systems. I build techniques to improve the efficiency of datacenter applications, provide systems support for heterogeneous platforms, verify the safety of complex distributed systems, analyze and fix failures, and improve the security of modern hardware. Building efficient and trustworthy systems requires a combination of approaches. My work draws insights from a broad set of disciplines such as systems, computer architecture, and programming languages.

\mysec{Education}

\mysub{Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL)}{}{Lausanne, Switzerland} \vspace*{1mm} \\
\myssub{\vspace{2mm}\textit{PhD in Computer Science}\hfill Sep. 2010--Dec. 2015 \\
Thesis: Techniques for Detection, Root Cause Diagnosis, \\ \phantom{xxxxxx} and Classification of In-Production Concurrency Bugs \\
Advisor: Prof. George Candea} \vspace{1mm}

\mysub{Middle East Technical University (METU)}{}{Ankara, Turkey} \vspace*{1mm} \\
\myssub{\vspace{2mm}\textit{M.Sc. in Electrical and Electronics Engineering} \hfill Sep. 2006--Jun. 2009 \\
Thesis:  Variability Modeling in Software Product Lines \\
{\textit{Graduated with the top grade}} \\
Advisor: Prof. Semih Bilgen} \vspace*{1mm}

\myssub{\textit{B.Sc. in Electrical and Electronics Engineering} \hfill Sep. 2002--Jun. 2006 \\
Project: Embedded Target Estimation, Detection, and Tracking\\
{\textit{Graduated with High Honors}} \\
Advisor: Prof. Arzu Koc}

\newpage

\mysec{Awards and Honors}
\myssub{DSN Rising Star in Dependability Award \hfill 2025} \\
\myssub{MLSys Best Paper Award \hfill 2025} \\
\myssub{AMD Faculty Research  Award \hfill 2024} \\
\myssub{Amazon Research Award \hfill 2024} \\
\myssub{Google Research Award \hfill 2024} \\
\myssub{Open Compute Research Award \hfill 2024} \\
\myssub{SIGCOMM Best Paper Award \hfill 2024} \\
\myssub{IEEE Micro Top Pick, ''Ocolos'' \hfill 2023} \\
\myssub{Google Research Award \hfill 2023} \\
\myssub{MICRO Best Paper Award\hfill 2022} \\
\myssub{Morris Wellman Endowed Professorship \hfill 2022} \\
\myssub{PLDI Distinguished Reviewer Award \hfill 2022} \\
\myssub{Microsoft Research Faculty Fellowship \hfill 2021} \\
\myssub{Google Fuzzing Research Award \hfill 2021} \\
\myssub{VMware Early Career Grant \hfill 2021} \\
\myssub{IEEE Micro Top Pick Honorable Mention, ''Agamotto'' \hfill 2021} \\
\myssub{NSF CAREER Award \hfill 2020} \\
\myssub{Intel Rising Star Award \hfill 2020} \\
\myssub{IEEE Micro Top Pick Honorable Mention, ''NDA'' \hfill 2020} \\
\myssub{Google Faculty Research Award \hfill 2019} \\
\myssub{IEEE Micro Top Pick, ''Foreshadow'' \hfill 2019} \\
\myssub{Intel Faculty Award \hfill 2019} \\
\myssub{Jay Lepreau Best Paper Award, OSDI \hfill 2018} \\
\myssub{Intel Faculty Award \hfill 2018} \\
\myssub{Microsoft Azure Cloud Computing Award \hfill 2017} \\
\myssub{Outstanding Reviewer Award, WWW \hfill 2017} \\
\myssub{Patrick Denantes Memorial Prize for outstanding PhD thesis, EPFL \hfill 2016} \\
\myssub{EuroSys Roger Needham Award for Best PhD. Thesis in Computer Systems in Europe \hfill 2016} \\
\myssub{Intel Corp. Software and Services Group, Grant \hfill 2014--2016} \\
\myssub{VMware Inc., Doctoral Fellowship \hfill 2014--2015} \\
\myssub{EPFL, Doctoral Fellowship \hfill 2010--2011} \\
\myssub{Scientific and Technological Research Council of Turkey, Master Scholarship \hfill 2006--2008} \\


\mysec{Student Awards and Honors}

\myssub{ACM SIGARCH/IEEE CS TCCA Outstanding Dissertation Award, Tanvir Ahmed Khan \hfill 2024} \\
\myssub{NSF Graduate Research Fellowship (GRFP), Matthew Giordano \hfill 2024} \\
\myssub{Towner Prize for Outstanding for Outstanding Ph.D. research, Tanvir Ahmed Khan \hfill 2024} \\
\myssub{NSF CSGrad4US Fellowship, Hannah Lin \hfill 2023} \\
\myssub{ACM Student Research Competition First Prize (MICRO), Kan Zhu \hfill 2022} \\
\myssub{Rackham Doctoral Fellowship, Tanvir Ahmed Khan \hfill 2022} \\
\myssub{Google Fellowship, Kevin Loughlin \hfill 2021} \\
\myssub{Facebook Fellowship, Marina Minkin \hfill 2021} \\
\myssub{Facebook Fellowship Finalist, Ian Neal \hfill 2021} \\
\myssub{ACM Student Research Competition First Prize (MICRO), Shixin Song \hfill 2021} \\
\myssub{CRA Outstanding Undergraduate Researcher Award Honorable Mention, Shixin Song \hfill 2021} \\
\myssub{CRA Undergraduate Awards, Honorable Mention, Shixin Song \hfill 2021} \\
\myssub{NSF Graduate Research Fellowship (GRFP), Kevin Loughlin \hfill 2020} \\
\myssub{Award for Excellence in Climate, Diversity, Equity, and Inclusion; Univ. of Michigan, Kevin Loughlin \hfill 2020} \\
\myssub{NSF Graduate Research Fellowship (GRFP), Andrew Loveless \hfill 2020} \\
\myssub{Facebook Fellowship Finalist, Tanvir Ahmed Khan \hfill 2020} \\
\myssub{ACM Student Research Competition First Prize (CGO), Nathan Brown \hfill 2020} \\
\myssub{Microsoft Research PhD Fellowship, Andrew Quinn \hfill 2017} \\
\myssub{NSF Graduate Research Fellowship (GRFP), Andrew Quinn \hfill 2017} \\


%% \myssub{Middle East Technical University, Dean's High Honor List \hfill 2006} \\
%% \myssub{Middle East Technical University, \\ Best Team Performance Award, Undergraduate Final Project  \hfill 2006} \\
%% \myssub{Turkish Customs Association, Scholarship \hfill 2002--2006} \\



\mysec{Funding}

Overall, I raised 10.346 million USD for my group’s research funding, including fellowships (82.344M total amount of funding).\\

\myssub{Samsung Advaned Technology Grant, 400K USD, PI \hfill 2025} \\
\myssub{DARPA TRACTOR Grant, 1M USD, PI \hfill 2025} \\
\myssub{AMD Faculty Research Award, 125K USD, PI \hfill 2024} \\
\myssub{Open Compute Project, 47.5K USD, PI \hfill 2024} \\
\myssub{Amazon Gift, 50K USD, PI \hfill 2024} \\
\myssub{SRC JUMP 2.0 SEED grant, 50K USD, PI \hfill 2024} \\
\myssub{IARPA-H, 400K USD (2M USD total), co-PI \hfill 2024} \\
\myssub{Google Gift, 50K USD, PI \hfill 2024} \\
\myssub{SRC JUMP 2.0 SEED grant, 80K USD, PI \hfill 2023} \\
\myssub{NSF Large, 1M USD (5M USD total), co-PI \hfill 2023} \\
\myssub{SRC JUMP 2.0 grant, 1M USD (35M USD total), PI \hfill 2023} \\
\myssub{Intel Transformative Server Architectures Center, 150K USD (600K USD total), PI \hfill 2022} \\
\myssub{Google Gift, 30K USD, PI \hfill 2022} \\

\myssub{ONR Grant, 510K USD, PI \hfill 2022} \\
\myssub{Morris Wellman Professorship Endowment, 40K USD, PI \hfill 2022} \\
\myssub{Google Fuzzing Research Award, 50K USD, PI \hfill 2021} \\
\myssub{Microsoft Research Faculty Fellowship, 200K USD, PI \hfill 2021} \\
\myssub{VMware Early Career Grant, 50K USD, PI \hfill 2021} \\
\myssub{SRC Realignment Grant, 406K USD, PI \hfill 2021} \\
\myssub{NSF CAREER Award, 576K USD, PI \hfill 2020} \\
\myssub{NSF/Intel FoMR Grant, 180K USD (360K USD total), co-PI \hfill 2020} \\
\myssub{NSF FMitF Grant, 375K USD (750K USD total), co-PI \hfill 2020} \\
\myssub{DARPA AMP Grant, 600K USD (1.8M USD total), PI \hfill 2020} \\
\myssub{SRC Seed Grant, 50K USD (150K USD total), PI \hfill 2020} \\
\myssub{Intel Rising Star Award, 50K USD, PI \hfill 2020} \\
\myssub{Intel Faculty Award, Performance Debugging, 75K USD, PI \hfill 2019} \\
\myssub{Google Cloud Computing Grant, 5K USD, PI \hfill 2019} \\
\myssub{Google Faculty Research Award, 80K USD, PI \hfill 2019} \\
\myssub{Intel Faculty Award, Automated Performance Optimization, 75K USD, PI \hfill 2018} \\
\myssub{Michigan College of Engineering Grant, 3K USD, PI \hfill 2018} \\
\myssub{Michigan Cambridge Research Initiative, 15K USD, PI \hfill 2018} \\
\myssub{Intel Gift, SysTEX'18 Workshop Sponsorship, 2K USD, PI \hfill 2018} \\
\myssub{Microsoft Azure Cloud Computing Grant, 25K USD, PI \hfill 2018} \\
\myssub{SRC JUMP 1.0 grant, 1,25M USD (31.2M USD total), PI \hfill 2017} \\

%% \mysec{Student Awards and Honors}
%% \myssub{NSF Graduate Research Fellowship (GRFP), Kevin Loughlin \hfill 2020} \\
%% \myssub{Award for Excellence in Climate, Diversity, Equity, and Inclusion; Univ. of Michigan, Kevin Loughlin \hfill 2020} \\
%% \myssub{NSF Graduate Research Fellowship (GRFP), Andrew Loveless \hfill 2020} \\
%% \myssub{Facebook Fellowship Finalist, Tanvir Ahmed Khan \hfill 2020} \\
%% \myssub{ACM Student Research Competition First Prize, Nathan Brown \hfill 2020} \\
%% \myssub{Microsoft Research PhD Fellowship, Andrew Quinn \hfill 2017} \\
%% \myssub{NSF Graduate Research Fellowship (GRFP), Andrew Quinn \hfill 2017} \\

\mysec{Employment}

\mysub{University of Washington}{}{Seattle, Washington, USA} \\
\myssub{Associate Professor\vspace{1mm} \hfill Aug. 2023-Present \\
  Paul G. Allen School of Computer Science \& Engineering}

\mysub{Google}{}{Seattle, Washington, USA} \\
\myssub{Faculty Researcher\vspace{1mm} \hfill Jun. 2022-Present \\
   Systems Research Group}

\mysub{University of Michigan}{}{Ann Arbor, Michigan, USA} \\
\myssub{Adjunct Associate Professor\vspace{1mm} \hfill Aug. 2023--Present \\
  Electrical Engineering and Computer Science Deparment}

\mysub{University of Washington}{}{Seattle, Washington, USA} \\
\myssub{Affiliate Associate Professor\vspace{1mm} \hfill Jun. 2022--Aug. 2023 \\
  Paul G. Allen School of Computer Science \& Engineering}

\mysub{University of Michigan}{}{Ann Arbor, Michigan, USA} \\
\myssub{Assistant Professor\vspace{1mm} \hfill Sep. 2017--Aug. 2023 \\
Electrical Engineering and Computer Science Deparment}

\mysub{Microsoft Research}{}{Cambridge, United Kingdom} \\
\myssub{\vspace{1mm}Researcher \hfill Aug. 2016--Aug. 2017 \\
Research on computer systems and networks}

\mysub{Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL)}{}{Lausanne, Switzerland} \\
\myssub{\vspace{1mm}Postdoctoral Researcher \hfill Dec. 2015--Jul. 2016 \\
Research on software security
\begin{itemize}
\item{I developed infrastructure that relies on hardware support to improve software security.}
\end{itemize}
}

\myssub{\vspace{1mm}Research Assistant \hfill Sep. 2010--Dec. 2015 \\
Research on software reliability with an emphasis on concurrent software
\vspace{-1mm}
\begin{itemize}
\setlength\itemsep{0em}
\item{I developed \textbf{Gist}, the first technique for accurately, efficiently, and automatically diagnosing the root causes of in-production failures, by using a combination of static and dynamic program analysis.}
\item{I developed \textbf{RaceMob}, the first automated in-production data race detection technique that can be kept always-on and provides high accuracy, by combining static data race detection with adaptive, crowdsourced dynamic data race detection.}
\item{I developed \textbf{Portend}, a high-accuracy technique to classify data races according to their potential consequences under arbitrary memory models, by using symbolic program analysis to explore multiple program paths and schedules to determine the effects of data races.}
\item{I developed \textbf{Bias-Free Sampling}, a technique that allows efficient sampling of rarely executed code (where bugs often lurk) without over-sampling frequently executed code, by using a new sampling algorithm and existing hardware support.}\\
\end{itemize}
\vspace{-5mm}
}


\mysub{Intel Corp.}{}{Santa Clara, CA, USA} \\
\myssub{\vspace{1mm}Research Intern \hfill Jul. 2015--Sep. 2015\\
Automated root cause diagnosis of failures and security enhancements using hardware support
\vspace{-1mm}
\begin{itemize}
\setlength\itemsep{0em}
\item{I developed a tool that allows developers to determine which program statements operate on a given data type at runtime using a mix of static program analysis and hardware support. In our experiments, this tool reduces the number of statements to examine during debugging by an order of magnitude. This tool is being extended internally at Intel.}
\item{I began investigating hardware support for enhancing system security, in particular, efficient path profiling for auditing and detecting control flow hijack attacks.}
\end{itemize}
\vspace{-2mm}
}



\mysub{VMware Inc.}{}{Palo Alto, CA, USA} \\
\myssub{\vspace{1mm}Research and Development Intern \hfill Jun. 2014--Sep. 2014\\
Automated debugging and runtime control flow tracking
\vspace{-1mm}
\begin{itemize}
\setlength\itemsep{0em}
\item{I implemented a runtime for efficient control flow tracking in software. This work formed the basis of my \textbf{Gist} work on root cause diagnosis.}
\item{I designed and implemented an infrastructure to remotely debug and profile VMware VCenter virtual machine management software, while it is running in production. This infrastructure is used by VCenter developers at VMWare.}
\end{itemize}
\vspace{-2mm}
}



\mysub{Microsoft Research}{}{Redmond, WA, USA} \\
\myssub{\vspace{1mm}Research Intern \hfill Jun. 2013--Sep. 2013\\
Efficient runtime execution sampling technique and low overhead coverage measurement
\vspace{-1mm}
\begin{itemize}
\setlength\itemsep{0em}
\item{I worked on the design of the \textbf{Bias-Free Sampling} framework for efficient runtime sampling. I designed and implemented the bias-free sampling framework for managed code (i.e., C\#). This tool is internally used at Microsoft.}
\item{I designed and implemented a fault injection tool to detect resource leakage problems using dynamic binary instrumentation. }
\end{itemize}
\vspace{-2mm}
}

\newpage

\mysub{Siemens Corporate Technology}{}{Istanbul, Turkey} \\
\myssub{\vspace{1mm}Senior Software Engineer \hfill Mar. 2008--May 2010 \\
Embedded home and industrial automation software
\vspace{-1mm}
\begin{itemize}
\setlength\itemsep{0em}
\item{I designed and implemented a real-time embedded gateway software between Siemens communication processors and a building automation system using C++ on top of VxWorks.}
\end{itemize}
}


\mysub{Aselsan Electronic Industries}{}{Ankara, Turkey} \\
\myssub{\vspace{1mm}Software Engineer \hfill May 2006--Mar. 2008 \\
Embedded motor control and functional testing infrastructure
\vspace{-1mm}
\begin{itemize}
\setlength\itemsep{0em}
\item{I was responsible for a real-time embedded control software for turret motor control. I also designed and implemented a full-system functional testing software using C++ on top of VxWorks for Power PC architectures.}
\end{itemize}
}

\myssub{Student Intern \hfill Jun. 2005--Jul. 2005 \\
Embedded software development
\vspace{-1mm}
\begin{itemize}
\setlength\itemsep{0em}
\item{I developed embedded control software for a night vision camera using C++ and PIC assembly on a PIC microcontroller.}
\end{itemize}
}



%\begin{spacing}{1.1}
\bibliographystyle{geo}
\begin{btSect}{header-standard,biblio-confs-journals}
\mysec{Peer-reviewed Publications}
\btPrintAll
\end{btSect}
%\end{spacing}


\mysec{Talks}
\begin{itemize}
  \setlength\itemsep{0em}
\item{Google} \hfill Apr 2024
\end{itemize}
\mysub{Profile Guided Processors}{}{}
\vspace{-2mm}
\begin{itemize}
  \setlength\itemsep{0em}
\item{Google} \hfill Dec 2023
\end{itemize}
\mysub{Tackling Silent Data Corruptions in the Data Center}{}{}
\vspace{-2mm}
\begin{itemize}
  \setlength\itemsep{0em}
\item{FOCI Summit (UW)} \hfill Oct 2023
\end{itemize}
\mysub{The Quest Towards Efficient and Trustworthy Systems}{}{}
\vspace{-2mm}
\begin{itemize}
  \setlength\itemsep{0em}
\item{ETH Zurich (Invited Talk, Workshop on Dependable and Secure Software Systems)} \hfill Oct 2022
\item{Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL)} \hfill May 2022
\item{Cornell University} \hfill April 2022
\item{University of Washington} \hfill April 2022
\item{Carnegie Mellon University} \hfill Feb 2022
\item{University of Texas at Austin} \hfill Feb 2022
\item{IEEE CITS (Keynote)} \hfill Nov 2021
\item{University of Wisconsin Madison (Invited Talk)} \hfill Sep 2021
\item{VMware (Invited Talk)} \hfill Jun 2021
\item{Intel (Invited Talk)} \hfill Jun 2021
\end{itemize}
\mysub{Optimizing the Front-end Performance of Modern Datacenter Servers}{}{}
\vspace{-2mm}
\begin{itemize}
  \setlength\itemsep{0em}
\item{Intel (Invited Talk)} \hfill Jun 2021
\end{itemize}
\mysub{Eliminating the Instruction Bottleneck in Modern Data Center Applications}{}{}
\vspace{-2mm}
\begin{itemize}
  \setlength\itemsep{0em}
\item{Intel (Invited Talk)} \hfill Mar 2021
\end{itemize}
\mysub{Eliminating Speculative Execution Vulnerabilities}{}{}
\vspace{-2mm}
\begin{itemize}
  \setlength\itemsep{0em}
\item{DARPA (Invited Talk)} \hfill Sep 2019
\end{itemize}
\mysub{Towards Continuous In-Production Failure Diagnosis}{}{}
\vspace{-2mm}
\begin{itemize}
  \setlength\itemsep{0em}
\item{Ohio State University (Invited Talk)} \hfill July 2018
\item{Greater Chicago Area Systems Research Workshop, University of Chicago (Invited Talk)} \hfill May 2018
\item{Purdue University (Invited Talk)} \hfill May 2018
\end{itemize}
\mysub{Hardware-Software Co-Design for Debugging and Performance Anlysis}{}{}
\vspace{-2mm}
\begin{itemize}
  \setlength\itemsep{0em}
  \item{Workshop on Resilient Systems, TU Dresden (Keynote)} \hfill Apr. 2017
\end{itemize}
\mysub{Symbolic Execution: A Gentle Introduction}{}{}
\vspace{-2mm}
\begin{itemize}
  \setlength\itemsep{0em}
  \item{Cyber In Bretagne Summer School (Invited Talk)} \hfill Jul. 2016
\end{itemize}

\mysub{Stamping Out Concurrency Bugs}{}{} 
\vspace{-2mm}
\begin{itemize}
\setlength\itemsep{0em}
\item{Royal Holloway, University of London, Seminar}\hfill Apr. 2016
\item{Georgia Institute of Technology, Seminar}\hfill Apr. 2016
\item{Carnegie Mellon University, Seminar}\hfill Apr. 2016
\item{University of Southern California, Seminar}\hfill Mar. 2016
\item{University of Rochester, Seminar}\hfill Mar. 2016
\item{Microsoft Research Redmond, Seminar}\hfill Mar. 2016
\item{Microsoft Research Cambridge, Seminar}\hfill Mar. 2016
\item{MPI Software Systems, Seminar}\hfill Mar. 2016
\item{University College London, Seminar}\hfill Mar. 2016
\item{Rice University, Seminar}\hfill Feb. 2016
\item{University of Toronto, Seminar}\hfill Feb. 2016
\item{University of Michigan, Seminar}\hfill Feb. 2016
\item{Boston University, Seminar}\hfill Feb. 2016
\item{Georgia Institute of Technology, Seminar}\hfill Feb. 2016
\item{VMWare Research, Seminar}\hfill Feb. 2016
\item{University of British Columbia, Seminar}\hfill Feb. 2016
\item{Simon Fraser University, Seminar}\hfill Jan. 2016
\end{itemize}

\mysub{Automated Root Cause Diagnosis of In-Production Failures}{}{} 
\vspace{-2mm}
\begin{itemize}
\setlength\itemsep{0em}
\item{Symposium on Operating System Principles (SOSP)}\hfill Oct. 2015
\item{Intel Corp.}\hfill Sep. 2015
\item{Google}\hfill Sep. 2015
\item{VMware Inc.}\hfill Sep. 2015
\end{itemize}


\mysub{Failure Sketches: A Better Way to Debug}{}{} 
\vspace{-2mm}
\begin{itemize}
\setlength\itemsep{0em}
\item{EcoCloud Annual Event}\hfill Jun. 2015
\item{Hot Topics in Operating Systems (HotOS)}\hfill May 2015
\end{itemize}


\mysub{Efficient Tracing of Cold Code via Bias-Free Sampling}{}{} 
\vspace{-2mm}
\begin{itemize}
\setlength\itemsep{0em}
\item{USENIX Annual Technical Conference (USENIX ATC)}\hfill Jun. 2014
\end{itemize}


\mysub{Lockout: Efficient Testing for Deadlock Bugs}{}{} 
\vspace{-2mm}
\begin{itemize}
\setlength\itemsep{0em}
\item{Workshop on Determinism and Correctness in Parallel Programming (WoDet)}\hfill Mar. 2014
\end{itemize}

\mysub{RaceMob: Crowdsourced Data Race Detection.}{}{} 
\vspace{-2mm}
\begin{itemize}
\setlength\itemsep{0em}
\item{Symposium on Operating System Principles (SOSP)}\hfill Oct. 2013
\item{EPFL Systems Seminar}\hfill Oct. 2013
\end{itemize}

\mysub{CoRD: A Collaborative Framework for Distributed Data Race Detection}{}{} 
\vspace{-2mm}
\begin{itemize}
\setlength\itemsep{0em}
\item{Workshop on Hot Topics in System Dependability (HotDep)} \hfill Oct. 2012
\end{itemize}

\mysub{Data Races vs. Data Race Bugs: Telling the Difference with Portend}{}{} 
\vspace{-2mm}
\begin{itemize}
\setlength\itemsep{0em}
\item{International Conference on Architectural Support for Programming Languages and \\ Operating Systems (ASPLOS)} \hfill Mar. 2012
\end{itemize}

\mysub{How to Build Reliable Software?}{}{} 
\vspace{-2mm}
\begin{itemize}
\setlength\itemsep{0em}
\item{Seminar talk to the incoming undergraduate students at EPFL} \hfill  Sep. 2011
\end{itemize}


\mysec{Professional Service}


\mysub{PC/Area Chair}{}{}\\
\myssub{\vspace{2mm}
  ASPLOS - Vice PC Chair \hfill 2026 \\ 
  MICRO - Datacenters, parallel architectures, Systems – Area Chair \hfill 2025 \\ 
  ICDCS - Operating Systems and Middleware - Track Chair \hfill 2025 \\ 
  ASPLOS Wild and Crazy Ideas Session (WACI) \hfill 2022 \\ 
  Workshop on Hot Topics In Operating Systems (HotOS) \hfill 2021 \\
  ACM Student Research Competition (ACM SRC), SOSP 2021 \hfill 2021 \\
  EuroSys Doctoral Workshop (Euro'DW) \hfill 2021 \\
  International Conference on Virtual Execution Environments (VEE) \hfill 2020 \\
  Workshop on System Software for Trusted Execution (SysTEX) (co-located with CCS'18) \hfill 2018 \\
  Symposium on Cloud Computing (SoCC) Poster Session \hfill 2018 \\
}
%

\mysub{PC Member}{}{}\\
\myssub{\vspace{2mm}
  IEEE MICRO Top Picks \hfill 2023 \\
  International Symposium on Computer Architecture (ISCA) \hfill 2023 \\
  Symp. on Operating System Design and Implementation (OSDI) \hfill 2020, 2021, 2022, 2023, 2024 \\
  Symp. on Operating Systems Principles (SOSP) \hfill 2019, 2023, 2024 \\
  Intl Conf. on Architectural Support for Programming Languages and Operating Systems (ASPLOS) \hfill 2021, 2022, 2023, 2025 \\
  International Conference on Learning Representations (ICLR) \hfill 2025\\
  Programming Language Design and Implementation (PLDI) \hfill 2022 \\
  Intl. Symp. on Microarchitecture (MICRO) \hfill 2022, 2024 \\
  EuroSys \hfill 2019, 2021 \\
  Intl. Conf. on Virtual Execution Environments (VEE) \hfill 2019 \\
  Intl. Conf. on Distributed Computing Systems (ICDCS) \hfill 2017, 2019 \\
  EuroSys Roger Needham PhD Award Committee \hfill 2019, 2022 \\  
  EuroSys Doctoral Workshop (EuroDW) \hfill 2018 \\
  Symp. on Cloud Computing (SoCC) \hfill 2018 \\
  World Wide Web Conference (WWW) \hfill 2017 \\
  Intl. Symp. on Software Testing and Analysis (ISSTA), Artifact Evaluation Committee \hfill 2014 \\
}\\

\mysub{Journal Reviewer}{}{} \\
\myssub{\vspace{2mm}Transactions on Architecture and Code Optimization \hfill 2018\\
  Transactions on Software Engineering \hfill 2015 \\
  Transactions on Software Engineering and Methodology \hfill 2015} \\

\mysub{Extended Review Committee}{}{}\\
\myssub{\vspace{2mm}
  Intl. Symp. on Microarchitecture (MICRO) \hfill 2021 \\
  Intl. Symp. on Computer Architecture (ISCA) \hfill 2021 \\
  Intl. Conf. on Architectural Support for Programming Languages and Operating Systems (ASPLOS) \hfill 2018 \\
}\\

\mysub{Shadow PC Member}{}{} \\ 
\myssub{\vspace{2mm}EuroSys Conference on Computer Systems (EuroSys) \hfill 2013, 2015} \\

\newpage

\mysub{External Reviewer}{}{} \\ 
\myssub{\vspace{2mm}Symp. on Operating Systems Principles (SOSP) \hfill 2011, 2013 \\
EuroSys Conf. on Computer Systems (EuroSys) \hfill 2011, 2012 \\
USENIX Annual Technical Conf. (USENIX ATC) \hfill 2011 \\
Intl. Conf. on Compiler Construction (CC) \hfill 2017 \\
Workshop on Hot Topics in Operating Systems (HotOS) \hfill 2011, 2013 \\
Conf. on Innovative Data Systems Research (CIDR)\hfill 2013\\
Intl. Conf. on Dependable Systems and Networks (DSN) \hfill 2011, 2013 \\
Symposium on Cloud Computing (SOCC) \hfill 2012 \\
Intl. SPIN Workshop on Model Checking of Software (SPIN) \hfill 2011} \\

\mysub{Committee Member}{}{} \\
\myssub{\vspace{2mm}University of Michigan, Computer Science and Engineering, DEI Committee \hfill 2021, 2022}\\
\myssub{University of Michigan, Computer Science and Engineering, Graduate Admissions Committee \hfill 2017--2022}\\
\myssub{OSDI Mentorship Arrangement Committee \hfill 2021}\\
\myssub{EPFL Doctoral School of Computer and Communication Sciences Audit Committee \hfill 2015}\\


\mysub{Panelist}{}{} \\
\myssub{\vspace{2mm}National Science Foundation \hfill 2019-Present}\\


\mysec{Teaching}
\mysub{Systems For All (CSE 550, UW)}{(graduate)}{\rm 2023, 2025\vspace{2mm}}\\
\mysub{Introduction to Operating Systems (EECS 482, Michigan)}{(undergraduate)}{\rm 2018, 2019, 2021, 2022\vspace{2mm}} \\
\mysub{Advanced Operating Systems (EECS 582, Michigan)}{(graduate)}{\rm 2017, 2019, 2020, 2021\vspace{2mm}} 

\mysec{Research Mentoring}

\mysub{Postdoc}{}{} \\

Yigong Hu \hfill Sep 2023-- \\
Rohan Kadekodi \hfill Sep 2023-- \\

\mysub{PhD}{}{} \\

Yufei Gao \hfill Sep 2025-- \\
Steven Gao \hfill Sep 2025-- \\
Maddie Burbage \hfill Sep 2023-- \\
Matthew Giordano \hfill Sep 2023-- \\
Michael Gu \hfill Sep 2023-- \\
Keisuke Kamahori \hfill Sep 2023-- \\
Haoran Peng \hfill Sep 2023-- \\
Dedong Xie \hfill Sep 2023-- \\
Kan Zhu \hfill Sep 2023-- \\
Andrew Quinn \hfill Sep 2020--Sep 2021 \\
Marina Minkin \hfill Sep 2020--Jan 2026 \\
Gefei Zuo \hfill Sep 2018--May 2024\\
Ian Neal \hfill Sep 2018--Jun 2023\\
Jiacheng Ma \hfill Sep 2018--Jan 2024\\
Andrew Loveless \hfill Sep 2018--Apr 2023\\
Kevin Loughlin \hfill Sep 2018--Aug 2023 \\
Tanvir Ahmed Khan \hfill Jan 2018--Jun 2023\\
Ofir Weisse \hfill Sep 2017--May 2020 \\

\mysub{Master's}{}{} \\
Muhammed Ugur \hfill Jan 2021--Jan 2023

\mysub{Undergraduate}{}{} \\

Yi Pan \hfill Mar 2025--\\
Qinyu Xu \hfill Mar 2024--\\
Haodong Zheng \hfill Jan 2024--\\
Yiyu Liu \hfill Jan 2024--\\
%%Shixin Song (ACM Student Research Competition Winner) \hfill Feb 2021-- \\
%%Haoyang Zhang \hfill Jun 2021--Jun 2022\\
%%Diane Tchiang \hfill May 2022--Jun 2023\\

\mysub{Alumni}{}{} \\

Yilong Zhao \hfill BSc $\rightarrow$ UC Berkeley PhD, 2024\\
Qinyu Xu \hfill BSc $\rightarrow$ Purdue PhD, 2024\\
Isaac Hou \hfill BSc $\rightarrow$ Michigan PhD, 2024\\
Tanvir Ahmed Khan \hfill PhD $\rightarrow$ Assistant Professor, Columbia University, 2024\\
Jiacheng Ma \hfill PhD $\rightarrow$ Software Engineer, AMD, 2024\\
Kevin Loughlin \hfill PhD $\rightarrow$ Software Engineer, Google, 2023\\
Ian Neal \hfill PhD $\rightarrow$ R\&D Engineer, Veridise, 2023\\
Andrew Loveless \hfill PhD $\rightarrow$ Research, NASA, 2023\\
Shuwen Deng \hfill PhD $\rightarrow$ Postdoc, Tsinghua University, 2023\\
Michael Gu \hfill MSc $\rightarrow$ UW PhD, 2023\\
Kan Zhu \hfill BSc $\rightarrow$ UW PhD, 2023\\
Diane Chiang \hfill BSc $\rightarrow$ UW MSc, 2023\\
Shixin Song \hfill BSc $\rightarrow$ MIT PhD, 2022\\
Haoyang Zhang \hfill BSc $\rightarrow$ UIUC PhD, 2022\\
Muhammed Ugur \hfill BSc $\rightarrow$ Yale PhD, 2022\\
Andrew Quinn \hfill PhD $\rightarrow$ Assistant Professor, UCSC, 2021  \\
Nathan Brown \hfill MSc $\rightarrow$ ARM, 2021 \\
Ben Stoler \hfill MSc $\rightarrow$ CMU PhD, 2021 \\
Yineng Yan \hfill MSc $\rightarrow$ UT Austin PhD, 2021 \\
Morgan Borjigin-Wang \hfill MSc $\rightarrow$ Google, 2021 \\
Ashfaqur Rahaman \hfill BSc $\rightarrow$ University of Utah PhD, 2021\\
Dexin Zhang \hfill MSc $\rightarrow$ USTC PhD, 2021 \\
Zhiqi Chen \hfill BSc $\rightarrow$ CMU MSc, 2020 \\
Yongwei Yuan \hfill BSc $\rightarrow$ Purdue PhD, 2020 \\
Ruiyang Zhu \hfill BSc $\rightarrow$ Michigan PhD, 2020 \\
Elisa Tsai \hfill BSc $\rightarrow$ Michigan PhD, 2020 \\
Ben Reeves \hfill MSc $\rightarrow$ Qumulo, 2020 \\
Ofir Weisse \hfill PhD $\rightarrow$ Google, 2020 \\
Upamanyu Sharma \hfill BSc $\rightarrow$ MIT PhD, 2020 \\
Yimeng Zhou \hfill BSc $\rightarrow$ Google, 2020 \\
Xiaohe Cheng \hfill BSc $\rightarrow$ Google, 2019 \\
John Wu \hfill MSc $\rightarrow$ Apple, 2019\\
Liran Xiao \hfill BSc $\rightarrow$ UCLA MSc, 2019 \\
Yifan Dai \hfill BSc $\rightarrow$ University of Wisconsin PhD, 2019 \\
Yifan Zhao \hfill BSc $\rightarrow$ UIUC PhD, 2019 \\

%% \myssub{\vspace{2mm}Andrew Loveless (Ph.D.) \hfill Sep. 2018--present\\
%% \begin{itemize}
%% \setlength\itemsep{0em}
%% \item{Andrew and I are working on techniques to build efficient fault tolerant mission critical systems.}
%% \end{itemize}
%% }

%% \myssub{\vspace{2mm}Jiacheng Ma (Ph.D.) \hfill Sep. 2018--present
%% \begin{itemize}
%% \setlength\itemsep{0em}
%% \item{Jiacheng and I are working on techniques to make heterogeneous computing platforms more usable in a cloud environment.}
%% \end{itemize}
%% }

%% \myssub{\vspace{2mm}Ian Neal (Ph.D.) \hfill Sep. 2018--present
%% \begin{itemize}
%% \setlength\itemsep{0em}
%% \item{Ian and I are working on building new file system data structures for future memory technologies. We are also working on novel defenses against microarchitectural side-channel attacks.}
%% \end{itemize}
%% }

%% \myssub{\vspace{2mm}Gefei Zuo (Ph.D.) \hfill Sep. 2018--present
%% \begin{itemize}
%% \setlength\itemsep{0em}
%% \item{Gefei and I are working on techniques to leverage the full potential of emerging heterogeneous computing platforms.}
%% \end{itemize}
%% }

%% \myssub{\vspace{2mm}Kevin Loughlin (Ph.D.) \hfill Aug. 2018--present
%% \begin{itemize}
%% \setlength\itemsep{0em}
%% \item{Kevin and I are working on novel side-channel attacks, defenses against microarchitectural side-channel attacks, and novel ways for authentication.}
%% \end{itemize}
%% }

%% \myssub{\vspace{2mm}Yifan Zhao (3\textsuperscript{rd} year undergraduate) \hfill May. 2018--present
%% \begin{itemize}
%% \setlength\itemsep{0em}
%% \item{Yifan and I are working on techniques to automatically detect and eliminate performance bugs in real-world systems.}
%% \end{itemize}
%% }

%% \myssub{\vspace{2mm}Tanvir Ahmed Khan (Ph.D.) \hfill Jan. 2018--present
%% \begin{itemize}
%% \setlength\itemsep{0em}
%% \item{Tanvir and I are working on building techniques to automatically detect and eliminate performance bugs in real-world systems.}
%% \end{itemize}
%% }

%% \myssub{\vspace{2mm}Ofir Weisse (Ph.D.) \hfill Sep. 2017--present
%% \begin{itemize}
%% \setlength\itemsep{0em}
%% \item{Ofir and I are working on making system security more useful and usable. We primarily focus on techniques to effectively and efficiently migrate legacy code into cloud environments, while improving security properties using a combination of system support and new hardware technologies.}
%% \end{itemize}
%% }

%% \myssub{\vspace{2mm}Lisa Zhou (1\textsuperscript{st} year Master's) \hfill Sep. 2015--Feb. 2016
%% \begin{itemize}
%% \setlength\itemsep{0em}
%% \item{Lisa and I worked on using hardware support for improving the security of software systems. In that regard, Lisa and Benjamin (see below) built a framework for reproducing security bugs in large applications (e.g., Chrome).}
%% \end{itemize}
%% }

%% \myssub{Benjamin Schubert (3\textsuperscript{rd} year undergraduate) \hfill Feb. 2015--Dec. 2015
%% \begin{itemize}
%% \setlength\itemsep{0em}
%% \item{Benjamin and I worked on a framework that enables reliably reproducing failures in systems software like Apache and MySQL. We used this framework to evaluate my \textbf{Gist} work on root cause diagnosis. We extended this framework to encompass security vulnerabilities.}
%% \end{itemize}
%% }

%% \newpage
%% \myssub{Ali Kheradmand (3\textsuperscript{rd} year undergraduate) \hfill Jul. 2013--Sep.2013
%% \begin{itemize}
%% \setlength\itemsep{0em}
%% \item{Ali and I worked on the \textbf{Lockout} project and developed a technique to systematically perturb program executions (without modifying program semantics) to increase the probability of deadlock manifestation. Ali is currently pursuing his Ph.D. at UIUC.}
%% \end{itemize}
%% }

%% \myssub{Radu Coman (Master's thesis) \hfill Jan. 2012--Sep. 2012
%% \begin{itemize}
%% \setlength\itemsep{0em}
%% \item{Radu and I surveyed common concurrency bug patterns in open source software. After we identified data races as a common bug pattern among the 100 bugs we looked at in Google Code, we built a static data race detector, which I used in my \textbf{RaceMob} project. Radu is currently a senior software engineer at Ixia.}
%% \end{itemize}
%% }

%% \mysec{Skills}

%% \myssub{Sharp learning curve, strong sense of responsibility and teamwork} \\
%% \myssub{Strong background in computer science and engineering, with an emphasis on operating systems, software engineering and VLSI design}\\
%% \myssub{Extensive knowledge of concurrency research and concepts} \\
%% \myssub{Extensive experience in real time embedded systems programming} \\
%% \myssub{{\em Languages:} C/C++, Java, C\#, Python, bash, HTML, XML, CSS, UML} \\
%% \myssub{{\em Tools:} Emacs, Rhapsody, Rose, Visual Studio, Netbeans, Eclipse, Tornado, Clearcase, git, subversion, gdb, SourceSafe, CVS, Doors, ClearDDTS, Quality Center, MPLAB}\\
%% \myssub{{\em Operating Systems:} VxWorks, Linux, Unix, Mac OS X, Windows, uCOS-II} \\
%% \myssub{{\em Hardware Platforms:}  x86, Motorola 68HC11, Microchip PIC, Power PC 603, FPGAs}



\mysec{Patents}
\mysub{Reverse Debugging of Software Failures}{}{\rm US Patent Number 10,565,511\vspace{2mm}} \\

\mysec{Languages}

%% \mysub{Hobbies}{}{}\\
%% \myssub{Athletics(track and field events), grip training, arm-wrestling, skiing}

\myssub{English: fluent \\
French: fluent \\
Turkish: native \\
German: beginner}\\

%% \mysec{References}

%% \myssub{Available upon request\\}

\end{document}
